\section{Related Work}
\label{sec:related_work}

\subsection{Multimodal Agentic Search}
The integration of active search has reframed LLMs from static knowledge bases into agentic reasoners capable of dynamic information retrieval. Search-R1~\citep{jin2025searchr1trainingllmsreason} crystallized this shift by using RL to incentivize autonomous, multi-turn querying within the reasoning chain. This paradigm has since migrated to multimodal domains; MMSearch-R1~\citep{mmsearch-r1} and Vision-DeepResearch~\citep{huang2026vision, deepmmsearch_r1} embed visual retrieval into agent pipelines, while recent efforts~\citep{zhang2025skywork, yao2026mm,chen2026unify,feng2026gen, li2025websailornavigatingsuperhumanreasoning} attempt to unify image manipulation with web search. However, a common but fragile assumption in these works is the availability of pristine visual inputs. In practice, when agents encounter degraded or text-dense real-world images, the "search-only" approach fails as retrieval cannot fix fundamentally broken visual evidence.

\subsection{Visual Perception and Retrieval}
The performance of multimodal agents is often bottlenecked not by retrieval logic, but by the fidelity of initial perception~\cite{zhang2026fix,wei2025perception}. While RAG frameworks like VisRAG~\citep{yu2024visrag} emphasize preserving visual structure, they treat the model as a passive observer that must "make do" with whatever is retrieved. Even as tool-augmented agents~\citep{song2026adareasonerdynamictoolorchestration, deepeyesv2, webwatcher} introduce dynamic orchestration, their toolsets remain largely homogeneous and scenario-bound. We argue that robust reasoning requires \emph{active perception}: the agent must not only search but also intervene—autonomously invoking tools like super-resolution or specialized OCR to remediate visual noise before attempting to reason over it.

\subsection{Reinforcement Learning for Agentic Reasoning}
Training agents to operate in long-horizon, multi-tool environments poses substantial challenges for standard RL. While GRPO~\citep{shao2024deepseekmath} has shown strong effectiveness in aligning reasoning trajectories for language models~\citep{guo2025deepseek,chen2025advancing,chen2025ares,feng2025video, feng2025onethinker, hu2026openvlthinkerv2generalistmultimodalreasoning}, applying it to agentic rollouts with diverse tool interactions remains non-trivial. The primary challenge lies in \textit{cascading failures}: an early tool error renders the rest of the trajectory incoherent~\citep{vuddanti2025paladin, zhu2025where, zheng2026deepeyesincentivizingthinkingimages,dong2025agenticreinforcedpolicyoptimization}, yet these post-failure tokens still inject noise into the policy gradient~\citep{REGRPO2025, deng2026group, CoRPO2025}. Furthermore, standard group-normalization tends to penalize the valid reasoning prefixes of partially successful rollouts~\citep{huang2026vision}. To counter this, we introduce a fatal-aware RL objective that prunes learning signals from post-failure states and uses one-sided advantage clamping to protect the gradients of constructive reasoning steps.

